Caveat Emptor: Light curves of the brightest stars in the \\ Southern sky as seen by bRing

### 2023-09-27 src/tex/ms.tex
[showyourwork] overleaf sync

%\documentclass[referee]{aa} % for a referee version
\documentclass[onecolumn]{aa} % for a paper on 1 column  
%\documentclass[longauth]{aa} % for the long lists of affiliations 
%\documentclass[letter]{aa} % for the letters 
%\documentclass{aa}

@@

   \title{Light curves of the brightest stars in the Southern sky\\ seen by bRing}

   \author{TBC Rosa Hoogenboom
          \inst{1}
          \and
          TBC Sanna Heesakkers
          \inst{1}
          \and
          TBC Matthew A. Kenworthy
          \inst{1}
          \and
          Remko Stuik
          \inst{1}
          \and
          Ignas Snellen
          \inst{1}
          \and
          Patrick Dorval
          \inst{1}
          }

@@

In the past years, the research of exoplanets expanded due to better instrumentation.
%
Because of this, more research could be conducted to search for exoplanets around bright stars.
%
In 2014 the Kepler K2 mission was launched to detect transits on stars with a magnitude brighter than 12 \citep{Howell_2014}.
%
Stars with $m_V<8$ could not be observed until the creation of the Multi-site All-Sky CAmeRA (MASCARA) \citep{mascara}.
%
When the MASCARA project was created in 2015 to detect exoplanets around stars with $8 > m_V > 4$ \citep{Talens_2017}, much brighter stars could be observed.
%
MASCARA uses long exposure times of 6.38 seconds to observe the sky which results in saturation of the pixels for stars with $m_V < 4$.
%
This changed in 2017 when the $\beta$ Pictoris b Ring project (bRing) \citep{bring} was introduced.
%
The MASCARA and bRing projects both use exposure times of 6.38 s.
%
However, bRing can also observe stars using an exposure time of 2.54 s.
%
Because of these short exposure times, bRing is able to collect data of stars with a magnitude brighter than 4 in the southern hemisphere.

According to the NASA Exoplanet Archive \citep{NASA_Exoplanet_Archive}, only 24 exoplanets have been found around stars with $m_V < 4$.
%
Only one of these stars, $\beta$ Pictoris, can be seen by bRing.
%
The bRing project can observe this star, because bRing was created to look at $\beta$ Pictoris specifically.
%
This small amount of discovered exoplanets suggests that there are still opportunities left to find new exoplanets around bright stars observed by bRing.

The aim of this research is to provide a catalogue of long-term light curves of the brightest stars in the southern hemisphere.
%
We use the data taken by the bRing cameras, for stars with a magnitude brighter than 4.
%
After creating light curves for the bright stars, we use the Transit Least Squares algorithm \citep{Hippke_2019} and Lomb-Scargle periodograms \citep{VanderPlas_2012,VanderPlas_2015} to try to find periodic signals in the data.
%
These periodic signals could imply variability of the star, eclipsing binaries, or even transiting exoplanets.

@@

\subsection{Reduction steps in the showyourwork framework}

Raw data is stored in a custom database and retrieved with Python 2.7 scripts on a local computer.

We extract the raw data for each camera and save as a FITS file with the format {\tt <HD number>\_<cameraID>.fits} where {\tt HD number} is the Henry Draper number for the star and {\tt cameraID} is one of the four camera names {\tt AUE,AUW,SAE,SAW}.
%
These raw data are written out using the {\tt save\_raw\_data\_from\_bring\_database.py} script.
%
The resulting 628 data files are 144 Gb in size and are retrievable from the public repository Zenodo at XXXXXX.

\subsection{Stars}
The bRing project can observe 157 bright stars with a magnitude brighter than 4.
%
154 of these stars are marked in red in the Hertzsprung-Russell (HR) diagram in \ref{HRD}. For the three missing stars, no parallax was found.
%
This HR diagram is made using data from an all-sky catalogue \citep{Kharchenko_2001}.
%
We use the parallaxes of the stars and their V and B magnitudes. The absolute magnitude is computed as follows:
\begin{align}
    M = m_V -5\log\left(\frac{1}{\pi}\right) + 5
\end{align}
$M$ is the absolute magnitude and $m_V$ is the apparent V-magnitude. $\pi$ is the parallax in arcseconds.
%
Most of the stars with a magnitude brighter than 4 are found in the upper part of the HR diagram, because they are all very bright.
%
A little over half of the bright stars lie on the main sequence and on the right of the main sequence a lot of giants can be found.
%
For reference, the Sun and Vega are also displayed in the figure.
%
Vega is one of the brightest stars in the northern hemisphere with a B-V colour of 0.
%
Using the B-V colour, the bright stars are found to have spectral type B to K.
%
A few stars have spectral type M. 
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/HR_final.png}
    \caption{This plot presents 154 of the 157 stars for which we make light curves in red.
      %
      The grey dots represent all of the stars which are observed by bRing.
      %
      The Sun is plotted in yellow and Vega in light blue (both of which are not observed by bRing).
      %
      On the vertical axis the absolute magnitude is displayed and on the horizontal axis the B-V colour scale is shown.}
    \label{HRD}
  \end{figure}

  Our data set contains multiple types of variable stars, which are described in \cite{Samus_2004}.
  %
  Variable stars can be divided in two categories: intrinsic and extrinsic variables.
  %
  Intrinsic variables change in brightness because of processes inside the star, like pulsating stars and eruptive variables, for instance.
  %
  Extrinsic variability is caused by external effects, for example by eclipses or rotation of the star.

  A noticeable portion of our stars are pulsating stars.
  %
  Pulsating stars expand and shrink, most times with a certain frequency. The gravitational force and radiation pressure in the star combat each other around hydrostatic equilibrium. As the star expands, the radiation pressure weakens, causing the star to shrink. As it becomes smaller, the radiation pressure increases. This causes the star to expand once again, repeating the cycle. As it pulsates, it emits more or less light, repeatedly.
Well-known pulsating stars are Cepheids, whose period is regular and related to their luminosity. Cepheids generally pulsate radially, which means that the whole star expands and contracts evenly. Other stars may pulsate non-radially, meaning that one part of the star expands while the other part shrinks. Beta Cephei variables are main-sequence stars, while Delta Cepheids are found on the instability strip, an evolutionary stage after the main sequence.

Pulsating giant or supergiant stars that have irregular periods ranging from weeks to years are known as long period variables. These are found on the right side of the HR diagram. Long period variables with regular periods are called Mira Ceti-type variables.

A few stars in our sample are rotating or eruptive stars. Rotating variables appear fainter or brighter when star spots come into view. These spots are cooler or warmer than the rest of the star, resulting in less or more light being emitted. Rotating stars can be main-sequence stars as well as giant stars, depending on which type of rotating star they are. Eruptive variables change in brightness irregularly due to eruptions on the surface of the star due to flares, for example. Some eruptive variables rotate as well, causing them to lose mass and appear fainter in consequence. These stars are called Gamma Cassiopeiae variables, which are all located on the main sequence in our data set.

Our sample contains a few eclipsing binaries as well. These are systems of multiple stars, which move in front of each other from our point of view and block the light of their companion. Depending on the combination of stars, a primary eclipse as well as a secondary eclipse can be seen. As one star moves in front of the other, part of the combined emitted light is obscured. When a fainter star moves in front of the brighter star, a primary eclipse occurs. The smaller eclipse is called a secondary eclipse, which takes place when the fainter star is covered by the brighter star.\\
Binary stars can be found in a wide range of ages and sizes, but their inclination and relative size determines whether eclipses can be seen. This means that they cannot be seen at an explicit position in the HR diagram.

\section{Methods}
\label{sec:methods}
\subsection{bRing}
The bRing project is based on the MASCARA project \citep{mascara} which takes images of the sky above airmass 2. However, while MASCARA uses five CCDs (facing north, south, east, west and central) to take images of the whole visible sky in the northern hemisphere, bRing uses only two (facing east and west). The bRing telescopes are situated in Australia and South Africa, thus positioned to look at the southern hemisphere ($\delta \leq -30 \degr $). The primary goal of the two projects also differs: MASCARA was created to search for transiting exoplanets around bright stars ($4 < m_V < 8$) and bRing was constructed to monitor the Hill sphere transit of exoplanet $\beta$ Pictoris b in front of the star $\beta$ Pictoris. The transit took place from April 2017 lasting 300 days until March 2018 \citep{Wang_2016}. Because of this period bRing started collecting data on 17 January 2017 \citep{bring}. Since this day data has been collected every night.

While observing $\beta$ Pictoris, bRing observes 20000 additional bright stars, because of the wide field of view ($\approx 53\degr$ ) around the star. The bRing project also monitors the atmospheric transmission and clouds. To capture both bright and relatively fainter stars, bRing uses two exposures times: 6.38 s for relatively faint stars ($4 < m_V < 8$) and 2.54 s for the brightest stars ($m_V < 4$). This results in a total of 13500 data points per day. These data points are calibrated every night by the bRing Control Software and sent to Leiden, the Netherlands.

\begin{figure}
    \centering
    \includegraphics[width=0.65\textwidth]{figures/bRing.jpg}
    \caption{The bRing instrument. Reprinted from \cite{bring}, figure 5.}
    \label{bRing}
\end{figure}

\subsection{Data reduction}
To make long-term light curves, we started with data reduction, which we wrote using Python 2.7.
The data reduction consists of multiple steps. For each step, we used the data of one of the 4 bRing cameras at a time. The primary calibration from \cite{Talens_2018} was applied.

We used two data sets which are described as ``daily" data and ``quarterly" data. The daily data consists of all data points collected by the bRing cameras. The quarterly data bins every 50 data points, resulting in at least 50 times fewer data points compared to the daily data. We mostly used the daily data, because bright stars have very little quarterly data. Because of saturation, these stars usually do not have enough data points to be binned.

For a star with no variability, the light curve is expected to be flat, because the amount of observed light is not expected to change. In reality, noise occurs because of outside effects such as clouds passing over the sky. This results in a distribution of data points around the mean value. To determine whether a data point should be rejected, the standard deviation was used. When removing data points based on standard deviation, we used the Astropy function \texttt{sigma\_clip}. The mean of the data set was calculated iteratively, discarding outliers each time. Based on the final calculated mean, outliers were removed from the data set. We also used this sigma-clipped-mean in further calculations when needed, instead of the mean which can be calculated before sigma-clipping.

We started the data reduction by selecting good data points from the daily and quarterly data. 
\begin{itemize}
    \item First, the long exposures were discarded. Only the short exposures were used, because the long exposures can only be used to observe stars fainter than magnitude 4. This is due to the fact that images taken with long exposure times have a higher chance of being saturated than the short exposures.
    \item Next, we used the astrometry and photometry flags of the daily data. These tell us if the measured flux is too high or too low to be realistic or if no photometry was performed due to the star being too close to the edge of the image, for example. Only the data without any bad flags was used. 
    \item We made sure that the magnitude error for the daily data is always greater than zero and finite, so no incorrect values are encountered. The magnitude values were also ensured to be finite.
    \item All data where the Sun is lower than $-18\degr$ was selected. This was added to ensure that the sky background did not get too bright. 
    \item Next, the data points where the cloud error was 3$\sigma$ above the mean cloud error were deleted. The 3$\sigma$ cutoff was estimated by eye. The cloud error tells us how the transmission changes over time; a big change might mean a cloud is in view. These outliers usually indicate that the clouds are variable at that point in time, in which case the data should not be used.
\end{itemize}
After selecting the good data points for the daily and quarterly data, the daily data was calibrated. However, we cannot use the daily data to remove, for example, the clouds, because those values are only available in the quarterly data. A piece of code written by Remko Stuik was applied to transfer the missing information from the quarterly data to the daily data. 
\begin{itemize}
    \item The 5$\sigma$ outliers based on magnitude error were discarded. A big error could mean that the measurement is wrong. 
    \item The 3$\sigma$ outliers for the mean of the clouds were also removed. This results in less background noise.
    \item The final step was to reject the 5$\sigma$ outliers for the mean of the sky background. This rejection also results in less background noise.
\end{itemize}

An example showing the different steps of the data reduction on a star has been provided below.

%teveel 'show'
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/delta_Cent_first3.png}
    \caption{The first three steps of the data reduction are shown here. The first plot shows the raw data that was saved by bRing. The second plot shows the data without the long exposures. Lastly, the data without the bad photometry and astrometry flags is plotted. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis.}
    \label{deltaCen1}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/delta_Cent_second3.png}
    \caption{This figure shows the next three steps of the data reduction. The first step is to make sure that the magnitude error is always finite and greater than zero. Next, the data where the altitude of the Sun is not below $-18^o$ is removed. In the last plot the 3$\sigma$ outliers on the mean of the cloud error are removed. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. Note that the magnitude scale is different for the last plot.}
    \label{deltaCen2}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/delta_Cent_last3.png}
    \caption{This figure shows the last three steps of the data reduction. First, the 5$\sigma$ outliers of the mean of the magnitude error are removed. In the second plot the 3$\sigma$ outliers on the mean of the cloud are removed. Lastly, the 5$\sigma$ outliers on the sky background are removed. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. Note that the magnitude scale differs for each plot.}
    \label{deltaCen3}
\end{figure}

\subsection{Detrending}
After performing data reduction, the data needed to be detrended. Detrending is the removal of trends in the data due to effects not caused by the star itself. For daily trends the effects are caused by the irregular shape of the point spread function, which changes the amount of light within the photometric aperture. For monthly trends the effects are caused by over-dimming the data points when the moon is visible.

Three trends were removed: two daily trends, and the monthly trend caused by the moon. We performed detrending similar to the secondary calibration used in \cite{Talens_2018}.

In a day, 13500 exposures can be taken in total. Every exposure at the same local sidereal time is given a number, called LSTSEQ \citep{Talens_2018}. Each night, the star should make the same path on the CCD. Detrending removes the effects caused by the same pixel receiving less or more light consistently. For every unique LSTSEQ, a sigma-clipped mean can be found. Subtracting this mean at every LSTSEQ removes this particular trend. We detrended this trend per year, because the transmission changes slightly over time.

The detrending of the second daily trend removes the effects caused by the Sun rising and setting. The sky background changes because of this. We divided a day in 500 bins, and determined the sigma-clipped mean of the data points in each bin. Each time sigma-clipping is used for detrending, the default values of 3$\sigma$, to reject data points, and 5 iterations are applied. The mean was then subtracted from all data points in one bin.

The last trend we removed is the one caused by the moon, which changes the sky background as well. The synodic period of the moon\footnote{The synodic period of the moon is 29.530588853 days.} and 25 bins per day were used to find a sigma-clipped mean per bin. This mean was subtracted from the data points in the bin.

For each step in the detrending process, the offsets calculated in the previous step were added.

For variable stars with a known period, we detrended the data by period folding and binning, similarly to the methods described above. Period folding is the process of overlapping the data points in regular intervals. The offset gained from this step was added back in after all other detrending steps, to regain the information about a stars' period.

@@

\section{Searching for periodic signals}
\label{sec:tlslomb}
Using the refined light curves, periodic signals could be found. Two methods were used for this. The Transit Least Squares algorithm was used to find transits in the light curves and the Lomb-Scargle periodograms were used to find sinusoidal periodic signals in the data.

Once a signal was found, a period fold was used to determine the validity of the signal. Using a period fold, the shape of the periodic behaviour can be found.

\section{Results}
\label{sec:results}
Using the bRing cameras, the 157 brightest stars ($m_V < 4$) in the southern hemisphere were observed. After performing data reduction, the trends caused by external effects in the data were removed. This process is called detrending. We removed two daily trends and the monthly trend caused by the moon. After this, light curves of these stars were generated. Finally, periodic signals could be found using these light curves. If these signals appeared to be transits or eclipses, the Transit Least Squares algorithm \citep{Hippke_2019} was applied. For variable stars such as pulsating or rotating stars, Lomb-Scargle periodograms \citep{VanderPlas_2012} \citep{VanderPlas_2015} were used.

\subsection{10 brightest stars}
The light curves of the ten brightest stars on the southern hemisphere are presented here, in order of decreasing brightness. 
\begin{enumerate}
\item \ref{Canopus} shows the light curve of alpha Carinae, the second brightest star in the sky and the brightest star in the southern hemisphere. It is better known as Canopus. The light curve can be seen in.
\item \ref{Rigil_Kentaurus} shows the light curve of alpha Centauri A, the third brightest stars in the sky. It is also known as Rigil Kentaurus. It is part of the alpha Centauri system, which contains Proxima Centauri, the closest star known to the Sun. 
\item \ref{Achernar} presents the light curve of alpha Eridani, also known as Achernar.
\item \ref{Hadar} shows the light curve of beta Centauri, also called Hadar. This star is a Beta Cephei.
\item \ref{Acrux} presents the light curve of alpha Crucis, a binary star system also known as Acrux.
\item \ref{Mimosa} shows the light curve of beta Crucis, also known as Mimosa.
\item \ref{Shaula} shows the light curve of lambda Scorpii, also known as Shaula. This is a binary system, with a Beta Cephei as primary star.
\item \ref{Gacrux} displays the light curve of gamma Crucis, also called Gacrux.
\item \ref{Miaplacidus} shows the ninth brightest star, beta Carinae. It is also known as Miaplacidus.
\item \ref{Alnair} shows the final brightest star. This is alpha Gruis, also known as Alnair.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/Canopus_thesis.png}
    \caption{Light curve of Canopus after data reduction and detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The ASCC-number of Canopus is 2111805.}
    \label{Canopus}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/Rigil_Kentaurus_thesis.png}
    \caption{Light curve of Rigil Kentaurus after data reduction and detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The ASCC-number of Rigil Kentaurus is 2348878.}
    \label{Rigil_Kentaurus}
\end{figure}

>>>>

%\documentclass[referee]{aa} % for a referee version
%\documentclass[onecolumn]{aa} % for a paper on 1 column  
%\documentclass[longauth]{aa} % for the long lists of affiliations 
%\documentclass[letter]{aa} % for the letters 
\documentclass{aa}

@@

   \title{Caveat Emptor: Light curves of the brightest stars in the \\ Southern sky as seen by bRing}

   \author{Rosa Hoogenboom
          \inst{1}
          \and
          Sanna Heesakkers
          \inst{1}
          \and
          Matthew A. Kenworthy
          \inst{1}
          \and
          Remko Stuik
          \inst{1}
          \and
          Ignas Snellen
          \inst{1}
          \and
          Patrick Dorval
          \inst{1}
          }

@@

Long term photometric observations of the brightest stars in the sky is challenging: the large photon rate on even the smallest telescopes can saturate most modern electronic detectors that are optimised for flux rates typically a million times lower.
%
A second problem is the lack of calibration stars of similar brightness on the celestial sphere that enable photometric calibration with a typical surface density of one star per 25 square degrees for the naked eye stars.
%
All sky cameras used for tracking meteors can provide unsaturated photometry of the brightest stars but their small entrance pupil means that they are susceptible to scintillation noise, limiting the photometric precision.

The Beta Pictoris Ring \citep[BRING; ][]{Stuik_2014} project is a network of four cameras in two completely automated observatories designed to provide continuous calibrated photometry of the exoplanet host star Beta Pictoris.
%
The Hill sphere of the gas giant Beta Pictoris b transited the star in 2015--2016, and the BRING observations provided significant upper limits on the presence of circumplanetary material around the planet \citep{Kenworthy21}.
%
Unsaturated light curves are available up to a magnitude of 4, but the BRING cameras saturate for brighter stars near the zenith.
%
At higher airmasses the atmospheric extinction allows the brightest stars to become unsaturated, and combined with the all-sky photometric calibration pipeline used for the MASCARA and BRING telescopes, the unsaturated data can be extracted to form light curves covering the duration of the BRING project, currently 2015 to 2022.

This paper presents long term photometric light curves for all naked sky stars visible from the Southern hemisphere.
%
In Section \ref{sec:obs} we summarise the raw data and initial data pipeline.
%
We then discuss the filters we use to remove saturated photometry and to correct for the known systematics in the BRING observatory.
%
In Section \ref{sec:methods}

% In 2014 the Kepler K2 mission was launched to detect transits on stars with a magnitude brighter than 12 \citep{Howell_2014}.
% %
% Stars with $m_V<8$ could not be observed until the creation of the Multi-site All-Sky CAmeRA (MASCARA) \citep{mascara}.
% %
% When the MASCARA project was created in 2015 to detect exoplanets around stars with $8 > m_V > 4$ \citep{Talens_2017}, much brighter stars could be observed.
% %
% MASCARA uses long exposure times of 6.38 seconds to observe the sky which results in saturation of the pixels for stars with $m_V < 4$.
% %
% This changed in 2017 when the $\beta$ Pictoris b Ring project (bRing) \citep{bring} was introduced.
% %
% The MASCARA and bRing projects both use exposure times of 6.38 s.
% %
% However, bRing also observes stars using an exposure time of 2.54 s.
% %
% Because of these short exposure times, bRing is able to collect data of stars with a magnitude brighter than 4 in the southern hemisphere.

% The bRing project can observe this star, because bRing was created to look at $\beta$ Pictoris specifically.
% %
% This small amount of discovered exoplanets suggests that there are still opportunities left to find new exoplanets around bright stars observed by bRing.

% The aim of this research is to provide a catalogue of long-term light curves of the brightest stars in the southern hemisphere suitable for research into stellar pulsations, variable stars and eclipsing systems.

%
% We use the data taken by the bRing cameras, for stars with a magnitude brighter than 4.
% %
% After creating light curves for the bright stars, we use the Transit Least Squares algorithm \citep{Hippke_2019} and Lomb-Scargle periodograms \citep{VanderPlas_2012,VanderPlas_2015} to try to find periodic signals in the data.
% %

@@

\section{Observations}\label{sec:obs}

\subsection{bRing}

The bRing project is based on the MASCARA project \citep{mascara} which takes images of the sky above airmass 2.
%
However, while MASCARA uses five CCDs (facing north, south, east, west and central) to take images of the whole visible sky in the northern hemisphere, bRing uses only two (facing east and west).
%
The bRing telescopes are situated in Australia and South Africa, thus positioned to look at the southern hemisphere ($\delta \leq -30 \degr $).
%
The primary goal of the two projects also differs: MASCARA was created to search for transiting exoplanets around bright stars ($4 < m_V < 8$) and bRing was constructed to monitor the Hill sphere transit of exoplanet $\beta$ Pictoris b in front of the star $\beta$ Pictoris.
%
The transit took place from April 2017 lasting 300 days until March 2018 \citep{Wang_2016}.
%
Because of this period bRing started collecting data on 17 January 2017 \citep{bring} and has continued every clear night since then.

While observing $\beta$ Pictoris, bRing observes 20000 additional bright stars and uses a custom pipeline to provide photometric calibration for the visible sky that accounts for several systematic effects.
%
The bRing project also monitors the atmospheric transmission and clouds.
%
To capture both bright and relatively fainter stars, bRing uses two exposures times: 6.38 s for relatively faint stars ($4 < m_V < 8$) and 2.54 s for the brightest stars ($m_V < 4$). This results in a total of 13500 data points per day.
%
These data points are calibrated every night by the bRing Control Software and sent to Leiden, the Netherlands.

\begin{figure}
    \centering
    \includegraphics[width=0.90\columnwidth]{figures/bRing.jpg}
    \caption{The bRing instrument. Reprinted from \cite{bring}, figure 5.}
    \label{bRing}
\end{figure}

\subsection{The stars}

All stars were selected that have $m_V<4$ and have a declination < 30 degrees, resulting in 157 stars, marked in red in the Hertzsprung-Russell (HR) diagram in Figure~\ref{HRD}.
%
The majority of the stars with an apparent magnitude brighter than 4 are giants, found in the upper part of the HR diagram.
%
Only a few of them are main sequence or late type dwarfs.

\subsection{Data processing}

TODO get the script for the HR diagram and make sure it still runs.

The data processing from the observatory to the local computers are detailed in \citet{Stuik_2014}.
%
The raw photometric data for each star is stored in a custom database which can be queried and the data retrieved with Python 2.7 scripts.
%
Each star is observed with multiple cameras distributed across the two BRING observatories.
%
We extract the raw data for each camera and save as a FITS file with the format {\tt <HD number>\_<cameraID>.fits} where {\tt HD number} is the Henry Draper number for the star and {\tt cameraID} is one of the four camera names {\tt AUE,AUW,SAE,SAW}.
%
These raw data are written out using the {\tt save\_raw\_data\_from\_bring\_database.py} script.
%
The resulting 628 data files are 144 Gb in size and are retrievable from the public repository Zenodo at XXXXXX.

% %
% A little over half of the bright stars lie on the main sequence and on the right of the main sequence a lot of giants can be found.
% %
% For reference, the Sun and Vega are also displayed in the figure.
% %
% Vega is one of the brightest stars in the northern hemisphere with a B-V colour of 0.
% %
% Using the B-V colour, the bright stars are found to have spectral type B to K.
% % %
% A few stars have spectral type M. 
\begin{figure}
    \centering
    \includegraphics[width=0.90\columnwidth]{figures/HR_final.png}
    \caption{This plot presents 154 of the 157 stars for which we make light curves in red.
      %
      The grey dots represent all of the stars which are observed by bRing.
      %
      The Sun is plotted in yellow and Vega in light blue (both of which are not observed by bRing).
      %
      On the vertical axis the absolute magnitude is displayed and on the horizontal axis the B-V colour scale is shown.}
    \label{HRD}
  \end{figure}

\subsection{Rejection of points}

%To make long-term light curves, we started with data reduction, which we wrote using Python 2.7.
%
The data reduction consists of multiple steps.
%
For each step, we used the data of one of the 4 bRing cameras at a time.
%
The primary calibration from \cite{Talens_2018} was applied.
%
For each star, there are two data sets generated by the calibration called ``daily'' data and ``quarterly'' data.
%
The daily data consists of all data points collected by the bRing cameras, collected with a cadence of 6.35 seconds, enabling searches for short term photometric fluctuations.
%
The quarterly data bins the photometry to every 50 data points, enabling searches for long term trends.
%
We use the daily data since the bright stars have very little quarterly data due to the binning including saturated photometric points.

Variability is seen in the daily data due to several systematic effects.

%
This results in a distribution of data points around the mean value. To determine whether a data point should be rejected, the standard deviation was used.
%
When removing data points based on standard deviation, we used the Astropy function \texttt{sigma\_clip}.
%
The mean of the data set was calculated iteratively, discarding outliers each time.
%
Based on the final calculated mean, outliers were removed from the data set.
%
We also used this sigma-clipped-mean in further calculations when needed, instead of the mean which can be calculated before sigma-clipping.

We started the data reduction by selecting good data points from the daily and quarterly data using these constraints:

\begin{enumerate}
    \item All data points from the eastern Australian camera on 3 and 4 April 2018 and the eastern South African camera on 10 September 2020 were discarded due to significant outliers of unknown origin.
    \item The 2.35 second exposures were used.
    \item We used the astrometry and photometry flags of the daily data. 
    %
    These tell us if the measured flux is too high or too low to be realistic or if no photometry was performed due to, e.g., the star being too close to the edge of the image.
    %
    Only the data without any bad flags was used. 
    \item We made sure that the magnitude error for the daily data is always greater than zero and finite, so no incorrect values are encountered. 
    \item All data where the Sun is lower than $-18\degr$ was selected. %This was added to ensure that the sky background did not get too bright. 
    \item The data points where the cloud error was 3$\sigma$ above the mean cloud error were deleted.
    %
    The 3$\sigma$ cutoff was estimated by eye.
    %
    The cloud error tells us how the transmission changes over time; a big change might mean a cloud is in view.
    %
    These outliers usually indicate that the clouds are variable at that point in time, in which case the data should not be used.
\end{enumerate}

After selecting the data points that pass all these steps in both the daily and quarterly data, the daily data was calibrated.
%
We cannot use the daily data to remove, for example, the clouds, because those values are only available in the quarterly data, so the missing information was copied from the quarterly data to the daily data.

\begin{itemize}
    \item The 5$\sigma$ outliers based on magnitude error were discarded. %A big error could mean that the measurement is wrong. 
    \item The 3$\sigma$ outliers for the mean of the clouds were also removed. %This results in less background noise.
    \item The final step was to reject the 5$\sigma$ outliers for the mean of the sky background. %This rejection also results in less background noise.
\end{itemize}

The impact of each step of the reduction is shown in Figure~\ref{deltaCen1}.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/delta_Cent_first3.png}
    \caption{The first three steps of the data reduction are shown here. The first plot shows the raw data that was saved by bRing. The second plot shows the data without the long exposures. Lastly, the data without the bad photometry and astrometry flags is plotted. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis.}
    \label{deltaCen1}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/delta_Cent_second3.png}
    \caption{This figure shows the next three steps of the data reduction. The first step is to make sure that the magnitude error is always finite and greater than zero. Next, the data where the altitude of the Sun is not below $-18^o$ is removed. In the last plot the 3$\sigma$ outliers on the mean of the cloud error are removed. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. Note that the magnitude scale is different for the last plot.}
    \label{deltaCen2}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/delta_Cent_last3.png}
    \caption{This figure shows the last three steps of the data reduction. First, the 5$\sigma$ outliers of the mean of the magnitude error are removed. In the second plot the 3$\sigma$ outliers on the mean of the cloud are removed. Lastly, the 5$\sigma$ outliers on the sky background are removed. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. Note that the magnitude scale differs for each plot.}
    \label{deltaCen3}
\end{figure}

\subsection{Detrending}

After performing data reduction, the data needed to be detrended due to effects not caused by the star itself.
%
For daily trends the effects are caused by the varying shape of the point spread function and its illuimination of the lenslets on the bRing detector cameras, which changes the amount of light within the photometric aperture.
%
For monthly trends the effects are caused by the scattered light when the Moon is visible at the site.

Three trends were removed: two daily trends, and the monthly trend caused by the Moon.
%
We performed detrending similar to the secondary calibration used in \cite{Talens_2018}.

Typically 13500 exposures are taken in one night.
%
Every exposure at the same local sidereal time is given a number, referred to as the {\tt LSTSEQ} \citep{Talens_2018}.
%
During each night, the star should make the same path on the CCD and cross the same pixel at the same local hour angle.
%
Detrending removes the effects caused by the same pixel receiving less or more light consistently.
%
For every unique LSTSEQ, a sigma-clipped mean can be found.
%
Subtracting this mean at every LSTSEQ removes this particular trend.
%
We detrended this trend per year, because the transmission changes slightly over time due to envrionmental effects of the observatory warming and cooling leading to small misalignments, and to the accumulation of dust on the entrance windows.

The detrending of the second daily trend removes the effects caused by the Sun rising and setting.
%
We divided a day into 500 bins, and determined the sigma-clipped mean of the data points in each bin.
%
Five iterations of a sigma clipping altorithm with a threshold of 5 sigma are applied.
%
%Each time sigma-clipping is used for detrending, the default values of 3$\sigma$,  and 5 iterations are applied.
%
The mean was then subtracted from all data points in one bin.

The last trend we removed is the one caused by the moon, which changes the sky background.
%
Trends matched to the synodic period (29.5305 days) were fitted and removed.
%
%The synodic period of the moon\footnote{The synodic period of the moon is 29.530588853 days.} and 25 bins per day were used to find a sigma-clipped mean per bin. This mean was subtracted from the data points in the bin.

%For each step in the detrending process, the offsets calculated in the previous step were added.

At this stage, the light curve for each star has all known trends removed.

For variable stars with a known period, we removed the large amplitude periodic variations before carrying out the detrending listed ablove, and then added this offset back into the light curve after the reduction steps.

@@

% \section{Searching for periodic signals}
% \label{sec:tlslomb}

% Using the cleaned light curves, a search for periodic signals can be done.
% %
% Two methods were used for this. The Transit Least Squares algorithm was used to find transits in the light curves and the Lomb-Scargle periodograms were used to find sinusoidal periodic signals in the data.

% Once a signal was found, a period fold was used to determine the validity of the signal. Using a period fold, the shape of the periodic behaviour can be found.

\section{Results}
\label{sec:results}
% Using the bRing cameras, the 157 brightest stars ($m_V < 4$) in the southern hemisphere were observed. After performing data reduction, the trends caused by external effects in the data were removed. This process is called detrending. We removed two daily trends and the monthly trend caused by the moon. After this, light curves of these stars were generated. Finally, periodic signals could be found using these light curves. If these signals appeared to be transits or eclipses, the Transit Least Squares algorithm \citep{Hippke_2019} was applied. For variable stars such as pulsating or rotating stars, Lomb-Scargle periodograms \citep{VanderPlas_2012} \citep{VanderPlas_2015} were used.

\subsection{Representative light curves}
The light curves of the several brightest stars on the southern hemisphere are presented.

The brightest star you have.

Delta Pavonis.

Two interesting variable stars.

% \begin{enumerate}
% \item \ref{Canopus} shows the light curve of alpha Carinae, the second brightest star in the sky and the brightest star in the southern hemisphere. It is better known as Canopus. The light curve can be seen in.
% \item \ref{Rigil_Kentaurus} shows the light curve of alpha Centauri A, the third brightest stars in the sky. It is also known as Rigil Kentaurus. It is part of the alpha Centauri system, which contains Proxima Centauri, the closest star known to the Sun. 
% \item \ref{Achernar} presents the light curve of alpha Eridani, also known as Achernar.
% \item \ref{Hadar} shows the light curve of beta Centauri, also called Hadar. This star is a Beta Cephei.
% \item \ref{Acrux} presents the light curve of alpha Crucis, a binary star system also known as Acrux.
% \item \ref{Mimosa} shows the light curve of beta Crucis, also known as Mimosa.
% \item \ref{Shaula} shows the light curve of lambda Scorpii, also known as Shaula. This is a binary system, with a Beta Cephei as primary star.
% \item \ref{Gacrux} displays the light curve of gamma Crucis, also called Gacrux.
% \item \ref{Miaplacidus} shows the ninth brightest star, beta Carinae. It is also known as Miaplacidus.
% \item \ref{Alnair} shows the final brightest star. This is alpha Gruis, also known as Alnair.

% \begin{figure}
%     \centering
%     \includegraphics[width=\textwidth]{figures/Canopus_thesis.png}
%     \caption{Light curve of Canopus after data reduction and detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The ASCC-number of Canopus is 2111805.}
%     \label{Canopus}
% \end{figure}

% \begin{figure}
%     \centering
%     \includegraphics[width=\textwidth]{figures/Rigil_Kentaurus_thesis.png}
%     \caption{Light curve of Rigil Kentaurus after data reduction and detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The ASCC-number of Rigil Kentaurus is 2348878.}
%     \label{Rigil_Kentaurus}
% \end{figure}
